%% Dr Alun Moon
%% assignment-template.tex, generated from assignment-template.dtx
\documentclass[12pt]{article}
\usepackage[british]{babel}

\usepackage{url}
\usepackage[round]{natbib}
\usepackage{infoboxes}

\usepackage{latexsym}
\usepackage{tlatex}
\usepackage{color}
\definecolor{boxshade}{gray}{.8}
\setboolean{shading}{true}

\usepackage{enumerate,
            siunitx}

\begin{document}

\section{Device communications register}
\subsection{The Specification} 
\begin{tla}
------------------------------- MODULE Device -------------------------------
CONSTANT Data
VARIABLE register

TypeInv == 
    register \in [ busy:{0,1}, data:Data ]

Init == 
    register = [busy|->0, data|-> CHOOSE x \in Data :TRUE ]

Send(d) ==
    /\ register.busy = 0
    /\ register' = [busy|->1, data|->d]

Read == 
    /\ register.busy = 1
    /\ register' = [register EXCEPT !.busy=0 ]

Next == 
    \/ \E d \in Data : Send(d)
    \/ Read 

Device == Init /\ [][Next]_register /\ WF_register(Next)
=============================================================================
\end{tla}
\begin{tlatex}
\@x{}\moduleLeftDash\@xx{ {\MODULE} Device}\moduleRightDash\@xx{}%
\@x{ {\CONSTANT} Data}%
\@x{ {\VARIABLE} register}%
\@pvspace{8.0pt}%
\@x{ TypeInv \.{\defeq}}%
 \@x{\@s{16.4} register \.{\in} [ busy \.{:} \{ 0 ,\, 1 \} ,\, data \.{:} Data
 ]}%
\@pvspace{8.0pt}%
\@x{ Init \.{\defeq}}%
 \@x{\@s{16.4} register \.{=} [ busy \.{\mapsto} 0 ,\, data \.{\mapsto}
 {\CHOOSE} x \.{\in} Data \.{:} {\TRUE} ]}%
\@pvspace{8.0pt}%
\@x{ Send ( d ) \.{\defeq}}%
\@x{\@s{25.84} \.{\land} register . busy \.{=} 0}%
 \@x{\@s{25.84} \.{\land} register \.{'} \.{=} [ busy \.{\mapsto} 1 ,\, data
 \.{\mapsto} d ]}%
\@pvspace{8.0pt}%
\@x{ Read \.{\defeq}}%
\@x{\@s{16.4} \.{\land} register . busy \.{=} 1}%
 \@x{\@s{16.4} \.{\land} register \.{'} \.{=} [ register {\EXCEPT} {\bang} .
 busy \.{=} 0 ]}%
\@pvspace{8.0pt}%
\@x{ Next \.{\defeq}}%
\@x{\@s{16.4} \.{\lor} \E\, d \.{\in} Data \.{:} Send ( d )}%
\@x{\@s{16.4} \.{\lor} Read}%
\@pvspace{8.0pt}%
 \@x{ Device \.{\defeq} Init \.{\land} {\Box} [ Next ]_{ register} \.{\land}
 {\WF}_{ register} ( Next )}%
\@x{}\bottombar\@xx{}%
\end{tlatex}

\section{The Model}

\subsection{Model Overview}
\paragraph{The Behaviour specification} is a \emph{Temporal formula} of
\begin{tla}
	Desvice
\end{tla}
\begin{tlatex}
\@x{\@s{32.8} Device}%
\end{tlatex}

\paragraph{The Model} values assigned to declared constants
\begin{tla}
	Data <- {0,1,2,3,4,5}
\end{tla}
\begin{tlatex}
\@x{\@s{32.8} Data \.{\leftarrow} \{ 0 ,\, 1 ,\, 2 ,\, 3 ,\, 4 ,\, 5 \}}%
\end{tlatex}

\subsection{Checks and verifications}
\paragraph{Invariants} The type-invariant is checked.
\begin{tla}
	TypeInv
\end{tla}
\begin{tlatex}
\@x{\@s{32.8} TypeInv}%
\end{tlatex}

\paragraph{Properties} the temporal property is checked: that the data is read
whenever it is available.
\begin{tla}
	[]<><<Read>>_register
\end{tla}
\begin{tlatex}
\@x{\@s{32.8} {\Box} {\Diamond} {\langle} Read {\rangle}_{ register}}%
\end{tlatex}

\subsection{Results} A summary of the results
\paragraph{Statistics} a summaries of the actions and number of states
found.

\begin{table}[h]
\begin{tabular}{lr}
	States found & \num{43} \\
 Distinct states & \num{12} \\ 
\end{tabular}
\end{table}

\begin{table}[h]
\begin{tabular}{llrr}
	\textbf{Action} & Location & States Found & \textbf{Distinct states} \\
	\hline
	\textit{Init}   & Line 8 & 1 & 1 \\
	\textit{Send}   & Line 11 & 36 & 6 \\
	\textit{Read}   & Line 15 & 6 & 5 \\
\end{tabular}
\end{table}

\subsection{Discussion}
\subsubsection{Model description} 
\paragraph{The state of the system is } Modelled as a record with fields
\texttt{busy} and \texttt{data}. 

\subparagraph{The type invariant} is that the busy flag can have a value of 0
and 1, and that the data can have a value from the constant Data.

\subparagraph{The initial conditions} 
set the busy flag to 0, and an arbitrary value from the Data is chosen.

\paragraph{The Next relation} is that there is some data value that can be
sent, or that the data is read

\paragraph{The system specification} is a conjunction of the initial
conditions, the next action with stuttering, and a weak fairness condition on
the next action.

\subsubsection{Interpretation of results}
The specification verifies under the model, satisfying the type invariant and
the temporal property;
\begin{tla}
	[]<><<Read>>_register
\end{tla}
\begin{tlatex}
\@x{\@s{32.8} {\Box} {\Diamond} {\langle} Read {\rangle}_{ register}}%
\end{tlatex}
This checks that data is continually read from the register: communication
happens.  We don't need to check a property on the Send action, as data may or
may not be sent.  But if it is sent, then we know t is read.



\end{document}

\endinput
%%
%% End of file `assignment-template.tex'.
